---
title: "Project Euler"
author: "G.Robertson"
date: "20/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Problem 1

```{r}
nums <- c(1:999)

results <- nums[nums%%3==0|nums%%5==0]

print(sum(results))
```


## Problem 2

Each new term in the Fibonacci sequence is generated by adding the previous two terms. By starting with 1 and 2, the first 10 terms will be:

1, 2, 3, 5, 8, 13, 21, 34, 55, 89, ...

By considering the terms in the Fibonacci sequence whose values do not exceed four million, find the sum of the even-valued terms.

### A bit of a cheeat because i couldn't figure out how to set a while condition of 'number<= 4000000'

Googled how to print the fibbonaci sequence (someone else's code), and with trying different terms I found out that the number of terms needed to take us up to 4 million is 34. 
Code below

```{r}
# take input from the user
nterms = 35
# first two terms
n1 = 0
n2 = 1
count = 2
# check if the number of terms is valid
if(nterms <= 0) {
print("Plese enter a positive integer")
} else {
if(nterms == 1) {
print("Fibonacci sequence:")
print(n1)
} else {
print("Fibonacci sequence:")
print(n1)
print(n2)
while(count < nterms) {
nth = n1 + n2
print(nth)
# update values
n1 = n2
n2 = nth
count = count + 1
}
}
}
```


So then I made the loop and stored the results in a vector
```{r}
fibbo <- c()
fibbo[1]=0
fibbo[2]=1

for (i in 3:34) {
      fibbo[i]=fibbo[i-1]+fibbo[i-2]
}

print(fibbo)
```
Now need to extract the even numbers and add them together
```{r}
evens <- fibbo[!fibbo%%2]

print(sum(evens))
```
This was correct.  
A much better solution was posted bu "nan.oliveira"
```{r}
sum <- 0
fib <- c(1, 1) 
while(fib[2] < 4000000){
  fib <- c(tail(fib, 1), sum(tail(fib, 2)))
  if (fib[2] %% 2 == 0) sum <- sum + fib[2]
}
print(sum)
```
